Visit Scotland Analysis

### 2023-07-05 visit_scotland_analysis.Rmd
Updates To Geospatial Aesthetics & README.md Screenshots

regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Domestic Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

@@

```{r}
regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_exp = mean(expenditure)) %>% 
  ggplot(aes(fill = mean_exp)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Expenditure of Domestic Vistors",
    subtitle = "By Region",
    fill = "Expenditure (Million GBP)") +
    theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

@@

```{r}
regional_data_joined %>%
  mutate(nights_per_visit = nights / visits) %>% 
  group_by(local_authority) %>% 
  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
  ggplot(aes(fill = mean_nights_per_visit)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Domestic Tourism Mean Nights per Visit",
    fill = "Mean Nights per Visit"
  ) +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(size = 15, face = "bold"))

@@

```{r}
regional_data_joined_sco_eng %>% 
  filter(region_of_residence == "Scotland") %>%
  group_by(local_authority) %>%
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Scottish Based Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

```{r}
regional_data_joined_sco_eng %>% 
  filter(region_of_residence == "England") %>% 
  group_by(local_authority) %>%
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "grey90", size = 0.5) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of English Based Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

>>>>

regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "white", linewidth = 0.04) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Domestic Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

@@

```{r}
regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_exp = mean(expenditure)) %>% 
  ggplot(aes(fill = mean_exp)) + 
  geom_sf(colour = "white", linewidth = 0.04) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Expenditure of Domestic Vistors",
    subtitle = "By Region",
    fill = "Expenditure (Million GBP)") +
    theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

@@

```{r}
regional_data_joined %>%
  mutate(nights_per_visit = nights / visits) %>% 
  group_by(local_authority) %>% 
  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
  ggplot(aes(fill = mean_nights_per_visit)) + 
  geom_sf(colour = "white", linewidth = 0.04) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Domestic Tourism Mean Nights per Visit",
    fill = "Mean Nights per Visit"
  ) +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(size = 15, face = "bold"))

@@

```{r}
regional_data_joined_sco_eng %>% 
  filter(region_of_residence == "Scotland") %>%
  group_by(local_authority) %>%
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "white", linewidth = 0.04) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Scottish Based Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

```{r}
regional_data_joined_sco_eng %>% 
  filter(region_of_residence == "England") %>% 
  group_by(local_authority) %>%
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "white", linewidth = 0.04) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of English Based Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```
